---
title: "7_Case characteristics"
author: "Laura Grajeda"
date: "10/25/2022"
output:
  html_document:
    toc: true
    toc_depth: 2
---




```{r include=FALSE}
library(tidyverse)
library(compareGroups)
library(lubridate)
```


# 1. Replicate frequencies of the characteristics of pneumonia cases


# 2. Data

Path
```{r}
#Path <- "C:/Users/lmg69188/OneDrive - University of Georgia/HAPIN/Pneumonia/Datos all IRCs/"
Path <- "C:/Users/lgrajeda/OneDrive - University of Georgia/HAPIN/Pneumonia/Datos all IRCs/"
```


**c42** This data set has information about vaccination
```{r}
c42<-list.files(path = paste0(Path, "Datos unblinded"), 
                   pattern = "hapin_pneumonia_c42",
                   full.names = TRUE) %>%
  tail(1) %>%
  haven::read_sas() 
```


**c30**
```{r}
setwd("C:/Users/lgrajeda/OneDrive - University of Georgia/HAPIN")
#setwd("C:/Users/lmg69188/OneDrive - University of Georgia/HAPIN")

# extraer la fecha de cuando los datos fueron descargados para incluirlo en el set de datos nuevos
dateDownload <- substring(list.files(path = "Pneumonia/Datos all IRCs/Datos unblinded", 
                   pattern = "hapin_pneumonia_c30_",
                   full.names = F), 23, 28)

c30<-list.files(path = "Pneumonia/Datos all IRCs/Datos unblinded", 
                   pattern = "hapin_pneumonia_c30_",
                   full.names = TRUE) %>%
  tail(1) %>%
  haven::read_sas() %>%
  filter(!is.na(c30_date)) %>% # seleccionar los registros con informacion
  mutate(c30_DateDownloaded = dateDownload) %>%
  rename("c30_timepoint" = timepoint)
```


**Pneumonia cases** This data set contains child-visits to health services and whether they met the pneumonia case definition. 
```{r}
PneumoDt <- read_rds(paste0(Path, "3_Pneumonia_Aplicar defincion de caso/Output/HAPIN_trt_Pneumonia_visits.rds"))
```






# 3. Prepare/create variables 


## 3.1 Demographic information


### Weight
```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_weight = case_when(
            !is.na(c36_Weight_cal) ~ c36_Weight_cal,
            is.na(c36_Weight_cal) & lead(DaysBtwVisit_cal)<=3 & !is.na(lead(c36_Weight_cal)) ~ lead(c36_Weight_cal)))
```



### Malnutrition
```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_malnutrition = case_when(
            c36_Malnutrition_zscore_cal==1 ~ c36_Malnutrition_zscore_cal,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_Malnutrition_zscore_cal)==1 ~ lead(c36_Malnutrition_zscore_cal),
            c36_Malnutrition_zscore_cal==0 ~ c36_Malnutrition_zscore_cal,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_Malnutrition_zscore_cal)==0 ~ lead(c36_Malnutrition_zscore_cal),
            TRUE ~ c36_Malnutrition_zscore_cal))

```


```{r}
PneumoDt %>%
  filter(hhid==44005) %>%
  select(hhid, Visit_date_cal, age_cal, c36_zwfl, c36_zwei , c36_Malnutrition_zscore_cal, Pneumonia)
```



### Up-to-date vaccination status
```{r}
# many has more than one c42 record
c42 %>% group_by(hhid) %>% count() %>% group_by(n) %>% count()
ids<-c42 %>% group_by(hhid) %>% count() %>% filter(n>1) %>% select(hhid) %>% t() %>% as.character()

c42 %>% filter(hhid %in% c(ids)) %>% select(hhid, c42_date, c42_pen1, c42_pen2, c42_pen3, c42_pen4)
```



```{r}

# see variables I am going to use
c42 %>%
  count(hhid, c42_pneumo_time, c42_penta_time, c42_measles_time)


# add date of birth to calculate age
c30_paraUnir <- c30 %>% select(hhid_blinded, c30_dob)
c42 <- c42 %>%
  merge(c30_paraUnir, by="hhid_blinded", all.x = T) %>% # calculate age
  mutate(c42_age_cal = interval(c30_dob, c42_date)/days())


# Remove those records without data.
c42 <- c42 %>% 
  filter(!is.na(c42_pneumo_time) | !is.na(c42_penta_time) | !is.na(c42_measles_time))


# See what is left
c42 %>% group_by(hhid) %>% count() %>% group_by(n) %>% count()
ids<-c42 %>% group_by(hhid) %>% count() %>% filter(n>1) %>% select(hhid) %>% t() %>% as.character()

# See repeated
c42 %>% 
  filter(hhid %in% c(ids))%>%
  count(hhid, c42_date, c42_pneumo_time, c42_pnm1, c42_pnm2, c42_pnm3, c42_pnm4)

#c42 %>% count(hhid_blinded, c42_age_cal)
```
Pneumococo
```{r}
c42 %>% count(hhid, c42_date, c42_pneumo_time, c42_pnm1, c42_pnm2, c42_pnm3, c42_pnm4)
```
Pentavalente
```{r}
c42 %>% count(c42_penta_time)
c42 %>% count(c42_penta_time, c42_pen1, c42_pen2, c42_pen3, c42_pen4, c42_pentavalent)
```
Measles
```{r}
a<-c42 %>% count(c42_measles_time)
a<-c42 %>% count(c42_measles_time, c42_mmr1, c42_mr1, c42_m2, c42_measles)
```


## 3.2 Clinical signs

### Temperature

```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_fever = case_when(
            c36_Fiebre_cal==1 ~ c36_Fiebre_cal,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_Fiebre_cal)==1 ~ lead(c36_Fiebre_cal),
            c36_Fiebre_cal==0 ~ c36_Fiebre_cal,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_Fiebre_cal)==0 ~ lead(c36_Fiebre_cal),
            TRUE ~ c36_Fiebre_cal))
```



### Pulse
```{r}
PneumoDt <- PneumoDt %>%
  mutate(pulse = rowMeans(PneumoDt %>% select(c36_pulse_60, c36_pulse_90, c36_pulse_120), na.rm=T),
         tb3_pulse = case_when(
            !is.na(pulse) ~ pulse,
            is.na(pulse) & lead(DaysBtwVisit_cal)<=3 & !is.na(lead(pulse)) ~ lead(pulse)))

PneumoDt %>% count(c36_pulse_60, c36_pulse_90, c36_pulse_120, tb3_pulse)
```
### Respiratory rate


```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_rr = case_when(
           c36_Tachypnea_cal==1 ~ c36_rr_cal,
           lead(c36_Tachypnea_cal)==1 & lead(DaysBtwVisit_cal)<=3 ~ lead(c36_rr_cal),
            !is.na(c36_rr_cal) ~ c36_rr_cal,
            is.na(c36_rr_cal) & lead(DaysBtwVisit_cal)<=3 & !is.na(lead(c36_rr_cal)) ~ lead(c36_rr_cal)))


PneumoDt %>% filter(hhid %in% c("23218", "23260", "23532", "23578", "33162", "33297", "33338")) %>%
  select(hhid, Visit_date_cal, c36_rr_cal, c36_Tachypnea_cal, Pneumonia, tb3_rr)
```

```{r}
a<-PneumoDt %>% filter(hhid %in% c("23218", "23260", "23532", "23578", "33162", "33297", "33338")) %>%
  select(hhid, Visit_date_cal, c36_rr_cal, c36_cough, c36_DificultadResp_cal, c36_CoughDifBre_cal, c36_hipoxemia_cal, c40_hipoxemia_cal, c41_hipoxemia_cal, AllPneumonia)
```


### Hypoxemia
```{r}
PneumoDt %>% count(c36_hipoxemia_cal, c40_hipoxemia_cal, c41_hipoxemia_cal)

PneumoDt <- PneumoDt %>%
  mutate(hypoxemia = case_when(c36_hipoxemia_cal==1 | c40_hipoxemia_cal==1 | c41_hipoxemia_cal==1 ~ 1,
                               c36_hipoxemia_cal==0 | c40_hipoxemia_cal==0 | c41_hipoxemia_cal==0~0),
         tb3_hypoxemia = case_when(
            hypoxemia==1 ~ hypoxemia,
            lead(DaysBtwVisit_cal)<=3 & lead(hypoxemia)==1 ~ lead(hypoxemia),
            hypoxemia==0 ~ hypoxemia,
            lead(DaysBtwVisit_cal)<=3 & lead(hypoxemia)==0 ~ lead(hypoxemia),
            TRUE ~ hypoxemia))

PneumoDt %>% count(c36_hipoxemia_cal, c40_hipoxemia_cal, c41_hipoxemia_cal, tb3_hypoxemia)
```



```{r}
a<-PneumoDt %>% filter(hhid %in% c("13019", "15055", "23503", "23583")) %>%
  count(hhid, Visit_date_cal, c36_hipoxemia_cal, c36_oxy_cal, c36_oxysup_cal, c36_oxy_route, c40_hipoxemia_cal, c41_hipoxemia_cal, Pneumonia, tb3_hypoxemia)
```




### Average SPO2.
```{r}
PneumoDt <- PneumoDt %>%
  mutate(c40oxy = matrixStats::rowMins(as.matrix(PneumoDt[,c("c40_oxy","c40_oxy_2","c40_oxy_3")]), na.rm=T),
         c40oxy = replace(c40oxy, c40oxy=="Inf", NA))



PneumoDt <- PneumoDt %>%
  mutate(
    oxy = matrixStats::rowMins(as.matrix(PneumoDt[,c("c36_oxy_ave", "c40oxy")]), na.rm=T),
    oxy = replace(oxy, oxy=="Inf", NA),
    tb3_oxy = case_when(
    c36_oxy_supplem==0 & ((oxy < 92 & irc!="Peru") | (oxy < 87 & irc=="Peru")) ~ oxy,
    lead(c36_oxy_supplem)==0 & ((lead(oxy) < 92 & irc!="Peru") | (lead(oxy) < 87 & irc=="Peru")) & lead(DaysBtwVisit_cal)<=3 ~ lead(oxy),
    c36_oxy_supplem==0 ~ oxy,
    lead(c36_oxy_supplem)==0 & lead(DaysBtwVisit_cal)<=3 ~ lead(oxy),
    (is.na(c36_oxy_supplem) | c36_oxy_supplem==1) & (c40_AnyOxySup_cal==0 | is.na(c40_AnyOxySup_cal)) & ((c40oxy<92 & irc!="Peru") | (c40oxy<87 & irc=="Peru"))  ~ c40oxy,
    (is.na(c36_oxy_supplem) | c36_oxy_supplem==1) & lead(c40_AnyOxySup_cal)==0 & 
      ((lead(c40oxy)<92 & irc!="Peru") | (lead(c40oxy)<87 & irc=="Peru")) & lead(DaysBtwVisit_cal)<=3 ~ lead(c40oxy),
    (is.na(c36_oxy_supplem) | c36_oxy_supplem==1) & c40_AnyOxySup_cal==0 ~ c40oxy,
    (is.na(c36_oxy_supplem) | c36_oxy_supplem==1) & lead(c40_AnyOxySup_cal)==0 & lead(DaysBtwVisit_cal)<=3 ~ lead(c40oxy),
    (is.na(c36_oxy_supplem) | c36_oxy_supplem==1) & c40_AnyOxySup_cal==1 ~ NA_real_,
    TRUE ~ NA_real_))


a<-PneumoDt %>%
  filter(Pneumonia==1) %>%
  arrange(c36_oxy_supplem) %>%
  count(hhid,c36_oxy_supplem, c36_oxy_ave, c40_AnyOxySup_cal, c40oxy, tb3_oxy)

PneumoDt %>%
  filter(hhid=="16130") %>%
  count(hhid, Visit_date_cal, DaysBtwVisit_cal, c36_oxy_supplem, c36_oxy_ave, c40_AnyOxySup_cal, c40oxy, tb3_oxy, Pneumonia)
```



```{r}
PneumoDt %>%
  filter(Pneumonia==1 & is.na(tb3_oxy)) %>%
  count(c36_oxy_supplem, c40_AnyOxySup_cal, tb3_oxy)
```

**20 are missing because child was on supplementary oxygen, 10 are missing because the information was not collected.**




### Wheeze

```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_wheez = case_when(
            c36_wheez_cal==1 ~ c36_wheez_cal,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_wheez_cal)==1 ~ lead(c36_wheez_cal),
            c36_wheez_cal==0 ~ c36_wheez_cal,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_wheez_cal)==0 ~ lead(c36_wheez_cal),
            TRUE ~ c36_wheez_cal))

```


### Respiratory danger sign

At least one respiratory danger sign, n (%): chest indrawing, severe chest indrawing, head nodding, persistent nasal flaring, grunting, stridor when calm, audible wheeze, tracheal tugging, intercostal recessions
```{r}
PneumoDt <- PneumoDt %>%
  mutate(RDS = case_when(
    c36_indraw==1 | c36_s_indraw==1 | c36_nodding==1 | c36_flaring ==1 | c36_grunt==1 | 
    c36_stridor==1 | c36_wheez==1 | c36_tugging==1 | c36_retraction==1 ~ 1,
    c36_indraw==0 | c36_s_indraw==0 | c36_nodding==0 | c36_flaring ==0 | c36_grunt==0 | 
    c36_stridor==0 | c36_wheez==0 | c36_tugging==0 | c36_retraction==0 ~ 0),
    tb3_RDS = case_when(
            RDS==1 ~ RDS,
            lead(DaysBtwVisit_cal)<=3 & lead(RDS)==1 ~ lead(RDS),
            RDS==0 ~ RDS,
            lead(DaysBtwVisit_cal)<=3 & lead(RDS)==0 ~ lead(RDS),
            TRUE ~ RDS))
```


### Chest indrawing
```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_indraw = case_when(
            c36_indraw==1 ~ c36_indraw,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_indraw)==1 ~ lead(c36_indraw),
            c36_indraw==0 ~ c36_indraw,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_indraw)==0 ~ lead(c36_indraw),
            TRUE ~ c36_indraw))
```

### Severe chest indrawing


```{r}
PneumoDt <- PneumoDt %>%
  mutate(s_indraw_2m = case_when(
    age_cal < 60 & c36_s_indraw==1 ~ 1,
    age_cal < 60 & c36_s_indraw==0 ~ 0,
    age_cal > 60 ~ NA_real_ ),
    tb3_s_indraw_2m = case_when(
            s_indraw_2m==1 ~ s_indraw_2m,
            lead(DaysBtwVisit_cal)<=3 & lead(s_indraw_2m)==1 ~ lead(s_indraw_2m),
            s_indraw_2m==0 ~ s_indraw_2m,
            lead(DaysBtwVisit_cal)<=3 & lead(s_indraw_2m)==0 ~ lead(s_indraw_2m),
            TRUE ~ s_indraw_2m))

PneumoDt %>% count(age_cal, tb3_s_indraw_2m)

# Que paso con esta edad?
PneumoDt %>% filter(age_cal== -52) %>% select(c30_dob, c36_h_date, c36_h_date_cal, c40_date_arrive_cal, c41_date_admit_cal, Pneumonia, irc)
```


### Head nodding
```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_nodding = case_when(
            c36_nodding==1 ~ c36_nodding,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_nodding)==1 ~ lead(c36_nodding),
            c36_nodding==0 ~ c36_nodding,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_nodding)==0 ~ lead(c36_nodding),
            TRUE ~ c36_nodding))
```


```{r}
PneumoDt %>% filter(hhid=="23260" | hhid=="33547") %>% select(hhid, Pneumonia, c36_nodding, Visit_date_cal, DaysBtwVisit_cal, tb3_nodding)
```



### Persistent nasal flaring
```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_flaring = case_when(
            c36_flaring==1 ~ c36_flaring,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_flaring)==1 ~ lead(c36_flaring),
            c36_flaring==0 ~ c36_flaring,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_flaring)==0 ~ lead(c36_flaring),
            TRUE ~ c36_flaring))
```


### Grunting
```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_grunt = case_when(
            c36_grunt==1 ~ c36_grunt,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_grunt)==1 ~ lead(c36_grunt),
            c36_grunt==0 ~ c36_grunt,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_grunt)==0 ~ lead(c36_grunt),
            TRUE ~ c36_grunt))
```


### Stridor when calm

```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_stridor = case_when(
            c36_stridor==1 ~ c36_stridor,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_stridor)==1 ~ lead(c36_stridor),
            c36_stridor==0 ~ c36_stridor,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_stridor)==0 ~ lead(c36_stridor),
            TRUE ~ c36_stridor))
```

### Audible wheeze

```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_awheez = case_when(
            c36_wheez==1 ~ c36_wheez,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_wheez)==1 ~ lead(c36_wheez),
            c36_wheez==0 ~ c36_wheez,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_wheez)==0 ~ lead(c36_wheez),
            TRUE ~ c36_wheez))
```




### Tracheal tugging
```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_tugging = case_when(
            c36_tugging==1 ~ c36_tugging,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_tugging)==1 ~ lead(c36_tugging),
            c36_tugging==0 ~ c36_tugging,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_tugging)==0 ~ lead(c36_tugging),
            TRUE ~ c36_tugging))
```



### Intercostal retractions

```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_retraction = case_when(
            c36_retraction==1 ~ c36_retraction,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_retraction)==1 ~ lead(c36_retraction),
            c36_retraction==0 ~ c36_retraction,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_retraction)==0 ~ lead(c36_retraction),
            TRUE ~ c36_retraction))
```



```{r}
PneumoDt %>% filter(hhid=="33547") %>% select(Visit_date_cal, c36_time, c36_location_cal, c36_retraction, Pneumonia)
```

### At least one general danger sign

```{r}
PneumoDt <- PneumoDt %>%
  mutate(DangerSign = case_when(
    age_cal < 60 & (c36_DangerSigns_cal==1 | c36_NeoDangerSigns_cal==1) ~ 1,
    age_cal < 60 & (c36_DangerSigns_cal==0 & c36_NeoDangerSigns_cal==0) ~ 0,
    age_cal >= 60 & c36_DangerSigns_cal==1 ~ 1,
    age_cal >= 60 & c36_DangerSigns_cal==0 ~ 0,
    TRUE ~ NA_real_ )) %>%
  mutate(tb3_dangerSign = case_when(
            DangerSign==1 ~ DangerSign,
            lead(DaysBtwVisit_cal)<=3 & lead(DangerSign)==1 ~ lead(DangerSign),
            DangerSign==0 ~ DangerSign,
            lead(DaysBtwVisit_cal)<=3 & lead(DangerSign)==0 ~ lead(DangerSign),
            TRUE ~ DangerSign))

PneumoDt %>%
  count(age_cal,c36_DangerSigns_cal, c36_NeoDangerSigns_cal, tb3_dangerSign)
```

### Unable to drink or breastfeed

```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_drink = case_when(
            c36_drink==1 ~ c36_drink,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_drink)==1 ~ lead(c36_drink),
            c36_drink==0 ~ c36_drink,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_drink)==0 ~ lead(c36_drink),
            TRUE ~ c36_drink))
```



### Vomiting everything, n 

```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_vomit = case_when(
            c36_vomit==1 ~ c36_vomit,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_vomit)==1 ~ lead(c36_vomit),
            c36_vomit==0 ~ c36_vomit,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_vomit)==0 ~ lead(c36_vomit),
            TRUE ~ c36_vomit))
```



### Convulsions

```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_convulsion = case_when(
            c36_convulsion==1 ~ c36_convulsion,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_convulsion)==1 ~ lead(c36_convulsion),
            c36_convulsion==0 ~ c36_convulsion,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_convulsion)==0 ~ lead(c36_convulsion),
            TRUE ~ c36_convulsion))
```


```{r}
PneumoDt %>% filter(hhid =="23218") %>% select(Visit_date_cal, c36_convulsion, c36_convulsion_2, Pneumonia)
```


### Lethargy or unconscious

```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_unconscious = case_when(
            c36_unconscious==1 ~ c36_unconscious,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_unconscious)==1 ~ lead(c36_unconscious),
            c36_unconscious==0 ~ c36_unconscious,
            lead(DaysBtwVisit_cal)<=3 & lead(c36_unconscious)==0 ~ lead(c36_unconscious),
            TRUE ~ c36_unconscious))
```


### Unable to feed well

```{r}
PneumoDt <- PneumoDt %>%
  mutate(feed_2m = case_when(
                age_cal < 60 & c36_feed==1 ~ 1,
                age_cal < 60 & c36_feed==0 ~ 0,
                age_cal > 60 ~ NA_real_ ),
        tb3_feed_2m = case_when(
            feed_2m==1 ~ feed_2m,
            lead(DaysBtwVisit_cal)<=3 & lead(feed_2m)==1 ~ lead(feed_2m),
            feed_2m==0 ~ feed_2m,
            lead(DaysBtwVisit_cal)<=3 & lead(feed_2m)==0 ~ lead(feed_2m),
            TRUE ~ feed_2m))

PneumoDt %>% count(age_cal, tb3_feed_2m)
```

### Not moving at all or moves only

```{r}
PneumoDt <- PneumoDt %>%
  mutate(move_2m = case_when(
    age_cal < 60 & c36_move==1 ~ 1,
    age_cal < 60 & c36_move==0 ~ 0,
    age_cal > 60 ~ NA_real_ ),
        tb3_move_2m = case_when(
            move_2m==1 ~ move_2m,
            lead(DaysBtwVisit_cal)<=3 & lead(move_2m)==1 ~ lead(move_2m),
            move_2m==0 ~ move_2m,
            lead(DaysBtwVisit_cal)<=3 & lead(move_2m)==0 ~ lead(move_2m),
            TRUE ~ move_2m))

PneumoDt %>% count(age_cal, tb3_move_2m)
```


## 3.3 Lung imaging

Lung ultrasound
```{r}
a<-PneumoDt %>% 
  filter(lus_pneumonia_final==1) %>%
  select(hhid_blinded, Visit_date_cal, lus_pneumonia_final, PneumoImage)

b <-PneumoDt %>%
  filter(Pneumonia==1 & lus_pneumonia_final==0) %>%
  select(hhid_blinded, Visit_date_cal, lus_pneumonia_final, PneumoImage)

c <- a %>%
  merge(b, by=c("hhid_blinded", "Visit_date_cal"), all = T) 

d<-c %>%
  group_by(hhid_blinded) %>%
  count(hhid_blinded) %>%
  filter(n>1) %>%
  t() %>%
  as.character()


c %>% 
  filter(hhid_blinded %in% c(d)) %>%
  arrange(hhid_blinded, Visit_date_cal) %>%
  group_by(hhid_blinded) %>%
  mutate(daysbetween = Visit_date_cal-lag(Visit_date_cal))

```

```{r}
PneumoDt <- PneumoDt %>%
  mutate(tb3_lus_pneumonia_final = case_when(
            lus_pneumonia_final==1 ~ lus_pneumonia_final,
            lead(DaysBtwVisit_cal)<=3 & lead(lus_pneumonia_final)==1 ~ lead(lus_pneumonia_final),
            lus_pneumonia_final==0 ~ lus_pneumonia_final,
            lead(DaysBtwVisit_cal)<=3 & lead(lus_pneumonia_final)==0 ~ lead(lus_pneumonia_final),
            TRUE ~ lus_pneumonia_final))
```



x rays


Negative xray read were not merge with visits because dont have date
```{r}
PneumoDt %>%
  filter(!is.na(xray_Final_read)) %>%
  count(xray_Final_read, xray_Image_date, Pneumonia, c36_date)


PneumoDt <- PneumoDt %>%
  mutate(tb3_xray_Final_read = case_when(
            xray_Final_read==1 ~ xray_Final_read,
            lead(DaysBtwVisit_cal)<=3 & lead(xray_Final_read)==1 ~ lead(xray_Final_read),
            xray_Final_read==0 ~ xray_Final_read,
            lead(DaysBtwVisit_cal)<=3 & lead(xray_Final_read)==0 ~ lead(xray_Final_read),
            TRUE ~ xray_Final_read))

```

## 3.4 Clinical care

Hospitalized

c36_after: 1=Discharged home,  2=Hospitalized, 3=Referred to another facility, 555=Other. C41_discharge_date minus C41_date_admit >= 1 (note: on C41 must be in facility for 1 or more days to be considered hospitalized).
```{r}
PneumoDt %>% count(c36_after, !is.na(c36_hospitalized))

PneumoDt %>% count(c41_location_cal, c41_FacilityType_cal)

PneumoDt <- PneumoDt %>% 
  group_by(hhid_blinded) %>%
  mutate(tb3_c41_Hospitalized = interval(c41_date_admit_cal, c41_discharge_date)/ddays(),
         tb3_hospitalized = case_when(
           c36_after==2 | tb3_c41_Hospitalized>=1 | (lead(DaysBtwVisit_cal)<=3 & lead(tb3_c41_Hospitalized)>=1) ~ 1,
           c36_after!= 2 | tb3_c41_Hospitalized ==0 ~ 0,
           TRUE  ~ NA_real_)) %>%
  ungroup(hhid_blinded)

# id with no possible hospitalizations
PneumoDt %>% 
  select(hhid, hhid_blinded, tb3_c41_Hospitalized, c41_date_admit_cal, c41_discharge_date, irc, c36_after) %>% 
  filter(tb3_c41_Hospitalized > 40 | tb3_c41_Hospitalized < 0) %>%
  arrange(tb3_c41_Hospitalized)


ids<-PneumoDt %>% filter((lead(DaysBtwVisit_cal)<=3 & lead(tb3_c41_Hospitalized)>=1)) %>%
  select(hhid) %>% t() %>% as.character()

a<-PneumoDt %>% filter(hhid %in% c(ids)) %>% select(hhid, Visit_date_cal, c41_date_admit_cal, c41_discharge_date, tb3_c41_Hospitalized, c36_after, tb3_hospitalized, Pneumonia) %>% arrange(hhid, Visit_date_cal)
```


Oxygen treatment
```{r}
# 
PneumoDt %>% count(c36_oxy_supplem)
PneumoDt %>%
  filter(c36_CRF=="c36") %>%
  count(c36_oxy_supplem, c36_oxy_supplem_R, c36_oxy_route)

PneumoDt %>%
  filter(c36_CRF=="c36a") %>%
  count(c36_oxy_supplem, c36_oxy_route)

PneumoDt %>% count(c40_oxygen)

PneumoDt %>% count(c40_oxygen_2)

PneumoDt %>% count(c40_receive)

PneumoDt %>% count(c40_receive_new1)

PneumoDt %>% count(c40_receive_2)

PneumoDt %>% count(c40_receive_new2)

PneumoDt %>% count(c41_oxygen_supplement, c41_oxygen_positive, c41_oxygen_mechanical)

a<-PneumoDt %>% count(c41_oxygen_2_supplement, c41_oxygen_2_positive, c41_oxygen_2_mechanical, c41_oxygen_2_highflownasal, c41_oxygen_2_nasal)


PneumoDt <- PneumoDt %>%
  mutate(OxyTx = case_when(
    c36_oxy_route==1 | c40_oxygen==1 | c40_oxygen_2 == 1 | c40_receive == 1 | c40_receive_new1 == 1 | c40_receive_2 == 1 | 
    c40_receive_new2 == 1 | c40_receive_3 == 1 | c40_receive_new3 == 1 | c41_oxygen_supplement== 1 | 
    c41_oxygen_2_supplement==1 | c41_oxygen_2_nasal==1 ~ 1,
    
    c36_oxy_route==2 | c36_oxy_route==3 | c36_oxy_route==4 | c36_oxy_supplem==0 | 
    c40_oxygen==0 | c40_oxygen==2 | 
    c40_oxygen_2 == 0 | c40_oxygen_2 == 2 | c40_oxygen_2 == 3 | c40_oxygen_2 == 4 |
    c40_receive == 0 | c40_receive == 2 |
    c40_receive_new1 == 0 | c40_receive_new1 == 2 | c40_receive_new1 == 3 | c40_receive_new1 == 4 |
    c40_receive_2 == 0 | c40_receive_2 ==2 |
    c40_receive_new2 == 0 | c40_receive_new2 == 2 | c40_receive_new2 == 3 | c40_receive_new2 == 4 |
    c40_receive_3 == 0 | c40_receive_3 ==2 |
    c40_receive_new3 == 0 | c40_receive_new3 == 2 | c40_receive_new3 == 3 | c40_receive_new2 == 3 |
    c41_oxygen_roomair == 1 | c41_oxygen_mechanical == 1 | c41_oxygen_positive==1 | 
    c41_oxygen_2_roomair == 1 | c41_oxygen_2_highflownasal == 1 | c41_oxygen_2_mechanical == 1 | c41_oxygen_2_positive==1 ~ 0,
    TRUE ~ NA_real_  ),
    tb3_oxyTx = case_when(
            OxyTx==1 ~ OxyTx,
            lead(DaysBtwVisit_cal)<=3 & lead(OxyTx)==1 ~ lead(OxyTx),
            OxyTx==0 ~ OxyTx,
            lead(DaysBtwVisit_cal)<=3 & lead(OxyTx)==0 ~ lead(OxyTx),
            TRUE ~ OxyTx))

PneumoDt %>%
  count(tb3_oxyTx)
```

**Advanced respiratory supportive care** Any of the following: High flow, NIV (CPAP/BiPAP), mechanical ventilation

```{r}
PneumoDt %>% count(c36_oxy_route)


PneumoDt <- PneumoDt %>%
  mutate(advOxyTx = case_when(
    c36_oxy_route==2 | c36_oxy_route==3 | c36_oxy_route==4 |
    c40_oxygen==2 | 
    c40_oxygen_2 == 2 | c40_oxygen_2 == 3 | c40_oxygen_2 == 4 |
    c40_receive == 2 |
    c40_receive_new1 == 2 | c40_receive_new1 == 3 | c40_receive_new1 == 4 |
    c40_receive_2 == 2 |
    c40_receive_new2 == 2 | c40_receive_new2 == 3 | c40_receive_new2 == 4 |
    c40_receive_3 == 2 |
    c40_receive_new3 == 2 | c40_receive_new3 == 3 | c40_receive_new3 == 4 |
    c41_oxygen_positive==1 | c41_oxygen_mechanical==1 |
    c41_oxygen_2_positive==1 | c41_oxygen_2_mechanical==1 | c41_oxygen_2_highflownasal==1 ~ 1,
    
    c36_oxy_supplem==0 | c36_oxy_route==1 |
    c40_oxygen==0 | c40_oxygen==1 |
    c40_oxygen_2 == 0 | c40_oxygen_2 == 1 |
    c40_receive == 0 | c40_receive == 1 |
    c40_receive_new1 == 0 | c40_receive_new1 == 1 |
    c40_receive_2 == 0 | c40_receive_2 == 1 |
    c40_receive_new2 == 0 | c40_receive_new2 == 1 |
    c40_receive_3 == 0 | c40_receive_3 == 1 |
    c40_receive_new3 == 0 | c40_receive_new3 == 1 |
    c41_oxygen_roomair == 1 | c41_oxygen_supplement==1 |
    c41_oxygen_2_roomair == 1 | c41_oxygen_2_nasal==1 | c41_oxygen_2_supplement==1 ~ 0,
    TRUE ~ NA_real_  ),
     tb3_advOxyTx = case_when(
            advOxyTx==1 ~ advOxyTx,
            lead(DaysBtwVisit_cal)<=3 & lead(advOxyTx)==1 ~ lead(advOxyTx),
            advOxyTx==0 ~ advOxyTx,
            lead(DaysBtwVisit_cal)<=3 & lead(advOxyTx)==0 ~ lead(advOxyTx),
            TRUE ~ advOxyTx))

PneumoDt %>%
  count(tb3_advOxyTx)

```

**Mortality** Death <30 days since diagnosis and/or Verbal Autopsy positive
```{r}
PneumoDt %>% count(va_pcvaCoD, !is.na(va_DateDownloaded), !is.na(e2_death_date))
PneumoDt %>% count(s6_Arm, va_DateDownloaded)

PneumoDt <- PneumoDt %>%
  group_by(hhid_blinded) %>%
  mutate(tb3_Death = ifelse(!is.na(e2_death_date),1,0),
         tb3_DeathWithin30days = case_when(
           tb3_Death==1 ~ 1,
           lead(DaysBtwVisit_cal<30) & lead(tb3_Death==1) ~ 1,
           tb3_Death==0 ~ 0,
           TRUE ~ NA_real_ )) %>%
  ungroup()

PneumoDt %>% 
  arrange(hhid_blinded, Visit_date_cal) %>%
  count(hhid, Visit_date_cal, DaysBtwVisit_cal)

ids <- PneumoDt %>% filter(tb3_Death==1) %>% select(hhid_blinded) %>% t() %>% as.character()
PneumoDt %>% filter(hhid_blinded %in% c(ids)) %>% 
  arrange(hhid_blinded, Visit_date_cal) %>%
  select(hhid_blinded, Visit_date_cal, DaysBtwVisit_cal, tb3_Death, va_pcvaCoD, tb3_DeathWithin30days)

```



# 4. Select pneumonia cases


```{r}
dt <- PneumoDt %>% 
  filter(Pneumonia==1)

write_rds(dt, "2022-12-15_HAPIN_Primary pneumonia cases.rds")
writexl::write_xlsx(dt, "2022-12-15_HAPIN_Primary pneumonia cases.xlsx")
```





# 5. Check each variable

Arm
```{r}
dt %>% count(s6_Arm)
dt$s6_Arm <- factor(dt$s6_Arm, levels = c(0,1), labels = c("Control", "Intervention"))
attr(dt$s6_Arm, "label") <- "Study arm"
```


## 5.1 Demogrphic information


### IRC
```{r}
dt %>% count(irc)
dt$irc <- factor(dt$irc)
attr(dt$irc, "label") <- "International Research Center"
```

Age
```{r}

dt <- dt %>%
  mutate(tb3_AgeGroup = factor(case_when(
    interval(c30_dob, Visit_date_cal)/days() < 60 ~ "<2",
    interval(c30_dob, Visit_date_cal)/days() < 180 ~ "2 to <6",
    interval(c30_dob, Visit_date_cal)/days() < 366 ~ "6 to <12")),
    interval= interval(c30_dob, Visit_date_cal)/days())

dt %>% count(age_cal, tb3_AgeGroup)
attr(dt$tb3_AgeGroup, "label") <- "Child's age (months)"


dt %>% filter(hhid=="33125") %>% select(c36_age_cal, tb3_AgeGroup, interval)
```


child sex
```{r}
dt %>% count(c30_sex)
dt$c30_sex <- factor(dt$c30_sex, levels = c(1,2), labels = c("male", "female"))
attr(dt$c30_sex, "label") <- "Child's sex"
```


### Weight
```{r}
dt %>% count(!is.na(c36_Weight_cal), !is.na(tb3_weight))
dt$tb3_weight <- as.numeric(dt$tb3_weight)
attr(dt$tb3_weight, "label") <- "Child's weight (Kg)"
```


### Severe acute malnutrition
```{r}
dt %>% count(c36_Malnutrition_zscore_cal, tb3_malnutrition)
dt$tb3_malnutrition <- factor(dt$tb3_malnutrition, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_malnutrition, "label") <- "Severe acute malnutrition"
```



### Up-to-date vaccination status


```{r}
c42_paraUnir <- c42 %>% select(hhid, hhid_blinded, c42_date, c42_age_cal, c42_pneumo_time, c42_penta_time, c42_measles_time)

dt2 <- dt %>%
  merge(c42_paraUnir, by=c("hhid", "hhid_blinded"), all.x = T)

dt2 %>% group_by(hhid, age_cal) %>% count() %>% filter(n>1)
```




```{r}
dt %>% filter(hhid=="13019") %>% select(hhid, irc, Visit_date_cal, Pneumonia, age_cal)
c42 %>% filter(hhid=="13019") %>% select(hhid, c42_date, c42_age_cal, c42_pneumo_time, c42_penta_time, c42_measles_time)

dt %>% filter(hhid=="23034") %>% select(hhid, irc, Visit_date_cal, Pneumonia, age_cal)
c42 %>% filter(hhid=="23034") %>% select(hhid, c42_date, c42_age_cal, c42_pneumo_time, c42_penta_time, c42_measles_time)

dt %>% filter(hhid=="24044") %>% select(hhid, irc, Visit_date_cal, Pneumonia, age_cal)
c42 %>% filter(hhid=="24044") %>% select(hhid, c42_date, c42_age_cal, c42_pneumo_time, c42_penta_time, c42_measles_time)
```



PM2.5, CO, BC

Antenatal PM2.5, CO, BC

Postnatal PM2.5, CO, BC

## 5.2 Clinical signs


### Temperature >38 C, n (%)
```{r}
dt %>% count(c36_Fiebre_cal, tb3_fever)
dt$tb3_fever <- factor(dt$tb3_fever, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_fever, "label") <- "Temperature >38°C"

dt %>% filter(c36_Fiebre_cal==0 & tb3_fever==1) %>% select(hhid)
```


### Average Heart rate

```{r}
dt %>% count(!is.na(tb3_pulse), !is.na(pulse))
attr(dt$tb3_pulse, "label") <- "Average heart rate (Beats per minute)"
```




### Average Respiratory rate
```{r}
dt %>% count(!is.na(tb3_rr), !is.na(c36_rr_cal))
attr(dt$tb3_rr, "label") <- "Average respiratory rate (Breaths per minute)"
```

### Average SPO2
```{r}
dt %>% count(!is.na(tb3_oxy), !is.na(oxy))
attr(dt$tb3_oxy, "label") <- "Average SpO2"
```



### Hypoxemia
```{r}
dt %>% count(tb3_hypoxemia, hypoxemia)
dt$tb3_hypoxemia <- factor(dt$tb3_hypoxemia, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_hypoxemia, "label") <- "Hypoxemia"

dt %>% filter(hypoxemia==0 & tb3_hypoxemia=="yes") %>% select(hhid)

a<-PneumoDt %>% filter(hhid %in% c("23218", "23260", "23578", "33119", "33166", "45024")) %>% 
  select(hhid, irc, Visit_date_cal, c36_oxy_ave, c40_oxy, c40_oxy_2, c40_oxy_3, hypoxemia, tb3_hypoxemia, oxy, tb3_oxy, Pneumonia) %>%
  arrange(hhid, Visit_date_cal)
```


### Wheeze +/- crackles, n (%)
In wheeze whether or not crackles present…
```{r}
dt %>% count(c36_wheez_cal, tb3_wheez)
dt$tb3_wheez<- factor(dt$tb3_wheez, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_wheez, "label") <- "Wheeze"


dt %>% filter(c36_wheez_cal==0 & tb3_wheez=="yes") %>% select(hhid)
```

### Respiratory danger sign
```{r}
dt %>% count(tb3_RDS, RDS)
dt$tb3_RDS <- factor(dt$tb3_RDS, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_RDS, "label") <- "Respiratory danger sign"


dt %>% filter(RDS==0 & tb3_RDS=="yes") %>% select(hhid)

```
### Chest indrawing, n (%)
```{r}
dt %>% count(tb3_indraw, c36_indraw)
dt$tb3_indraw <- factor(dt$tb3_indraw, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_indraw, "label") <- "Chest indrawing"

dt %>% filter(c36_indraw==0 & tb3_indraw=="yes") %>% select(hhid)
```


### Severe chest indrawing (Applies to <2 months only)
```{r}
dt %>%
  filter(age_cal <60) %>%
  count(tb3_s_indraw_2m, c36_s_indraw)

dt$tb3_s_indraw_2m <- factor(dt$tb3_s_indraw_2m, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_s_indraw_2m, "label") <- "Severe chest indrawing (only <2 months old)"
```



### Head nodding, n (%)**
```{r}
dt %>% count(tb3_nodding, c36_nodding)
dt$tb3_nodding <- factor(dt$tb3_nodding, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_nodding, "label") <- "Head nodding"


dt %>% filter(c36_nodding==0 & tb3_nodding=="yes") %>% select(hhid)
```


### Persistent nasal flaring, n (%)**
```{r}
dt %>% count(tb3_flaring, c36_flaring)
dt$tb3_flaring <- factor(dt$tb3_flaring, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_flaring, "label") <- "Persistent nasal flaring"
```


### Grunting, n (%)**
```{r}
dt %>% count(tb3_grunt, c36_grunt)
dt$tb3_grunt <- factor(dt$tb3_grunt, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_grunt, "label") <- "Grunting"
```


### Stridor when calm, n (%)**
```{r}
dt %>% count(tb3_stridor, c36_stridor)
dt$tb3_stridor <- factor(dt$tb3_stridor, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_stridor, "label") <- "Stridor when calm"

dt %>% filter(c36_stridor==0 & tb3_stridor=="yes") %>% select(hhid)

```


### Audible wheeze, n (%)**
```{r}
dt %>% count(tb3_awheez, c36_wheez)
dt$tb3_awheez <- factor(dt$tb3_awheez, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_awheez, "label") <- "Audible wheeze"

dt %>% filter(c36_wheez==0 & tb3_awheez=="yes") %>% select(hhid)
```


### Tracheal tugging, n (%)
```{r}
dt %>% count(c36_tugging, tb3_tugging)
dt$tb3_tugging <- factor(dt$tb3_tugging, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_tugging, "label") <- "Tracheal tugging"

dt %>% filter(c36_tugging==0 & tb3_tugging=="yes") %>% select(hhid)
```

### Intercostal retractions, n (%)
```{r}
dt %>% count(c36_retraction, tb3_retraction)
dt$tb3_retraction <- factor(dt$tb3_retraction, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_retraction, "label") <- "Intercostal retractions"

dt %>% filter(c36_retraction==0 & tb3_retraction=="yes") %>% select(hhid)
```

### At least one general danger sign
```{r}
dt %>% count(tb3_dangerSign, c36_DangerSigns_cal, c36_NeoDangerSigns_cal)
dt$tb3_dangerSign <- factor(dt$tb3_dangerSign, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_dangerSign, "label") <- "At least one general danger sign"


dt %>% filter((c36_DangerSigns_cal==0 | is.na(c36_DangerSigns_cal)) & (c36_NeoDangerSigns_cal==0 | is.na(c36_NeoDangerSigns_cal)) & tb3_dangerSign=="yes") %>% select(hhid)
```

### Unable to drink or breastfeed**
```{r}
dt %>% count(tb3_drink, c36_drink)
dt$tb3_drink <- factor(dt$tb3_drink, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_drink, "label") <- "Unable to drink or breastfeed"
```



### Vomiting everything
```{r}
dt %>% count(tb3_vomit, c36_vomit)
dt$tb3_vomit <- factor(dt$tb3_vomit, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_vomit, "label") <- "Vomiting everything"
```


### Convulsions
```{r}
dt %>% count(tb3_convulsion, c36_convulsion)
dt$tb3_convulsion <- factor(dt$tb3_convulsion, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_convulsion, "label") <- "Convulsions"

dt %>% filter(hhid=="23218") %>% select(tb3_convulsion)

dt %>% filter(c36_convulsion==0 & tb3_convulsion=="yes") %>% select(hhid)
```


### Lethargy or unconscious**
```{r}
dt %>% count(tb3_unconscious, c36_unconscious)
dt$tb3_unconscious <- factor(dt$tb3_unconscious, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_unconscious, "label") <- "Lethargy or unconscious"
```


### Unable to feed well
```{r}
dt %>% 
  filter(age_cal < 60) %>%
  count(c36_feed, tb3_feed_2m)
dt$tb3_feed_2m <- factor(dt$tb3_feed_2m, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_feed_2m, "label") <- "Unable to feed well (only <2 months old)"

dt %>% filter(age_cal < 60) %>%
  filter(c36_feed==0 & tb3_feed_2m=="yes") %>% select(hhid)
```


### Not moving at all or moves only
```{r}
dt %>% 
  filter(age_cal < 60) %>%
  count(c36_move, tb3_move_2m)
dt$tb3_move_2m <- factor(dt$tb3_move_2m, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_move_2m, "label") <- "Not moving at all or moves with stimulation only (only <2 months old)"


dt %>% filter(age_cal < 60) %>%
  filter(c36_move==0 & tb3_move_2m=="yes") %>% select(hhid)

```


## 5.3 Lung imaging

Lung ultrasound
```{r}
dt %>% count(lus_pneumonia_final, tb3_lus_pneumonia_final)
dt$tb3_lus_pneumonia_final <- factor(dt$tb3_lus_pneumonia_final, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_lus_pneumonia_final, "label") <- "Lung ultrasound"

dt %>% filter((lus_pneumonia_final==0 | is.na(lus_pneumonia_final)) & tb3_lus_pneumonia_final=="yes") %>% select(hhid)

```


Chest radiography
```{r}
dt %>% count(xray_Final_read, xray_Image_date)
dt$tb3_xray_Final_read <- factor(dt$tb3_xray_Final_read, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_xray_Final_read, "label") <- "Chest radiography"
```


## 5.4 Clinical care

**Hospitalized**
```{r}
dt %>% count(s6_Arm, tb3_hospitalized)
43/(43+41)
44/(37+44)
dt$tb3_hospitalized <- factor(dt$tb3_hospitalized, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_hospitalized, "label") <- "Hospitalized"

```

**Oxygen treatment**
```{r}
dt %>% count(tb3_oxyTx)
dt$tb3_oxyTx <- factor(dt$tb3_oxyTx, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_oxyTx, "label") <- "Oxygen treatment"
```

**Advanced respiratory supportive care** Any of the following: High flow, NIV (CPAP/BiPAP), mechanical ventilation
```{r}
dt %>% count(tb3_advOxyTx)
dt$tb3_advOxyTx <- factor(dt$tb3_advOxyTx, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_advOxyTx, "label") <- "Advance respiratory supportive care"
```


**Mortality** Death <30 days since diagnosis and/or Verbal Autopsy positive
```{r}
dt %>% count(tb3_DeathWithin30days)
dt$tb3_DeathWithin30days <- factor(dt$tb3_DeathWithin30days, levels = c(1,0), labels = c("yes", "no"))
attr(dt$tb3_DeathWithin30days, "label") <- "Death <30 days since diagnosis and/or Verbal Autopsy positive"
```




# 6. Create table



```{r}
cg1<-compareGroups(s6_Arm ~ irc + tb3_AgeGroup + c30_sex + tb3_weight + tb3_malnutrition,
                   data=dt,
                  method = 2, Q1 = 0, Q3 = 1,
                  include.label = T)

cg2<-compareGroups(s6_Arm ~ tb3_fever + tb3_pulse + tb3_rr + tb3_oxy + tb3_hypoxemia + tb3_wheez + 
                     tb3_RDS + tb3_indraw + tb3_s_indraw_2m + tb3_nodding + tb3_flaring + tb3_grunt +
                     tb3_stridor + tb3_awheez + tb3_tugging + tb3_retraction + tb3_dangerSign + tb3_drink + 
                     tb3_vomit + tb3_convulsion + tb3_unconscious + tb3_feed_2m + tb3_move_2m, 
                  data=dt,
                  method = 2, Q1 = 0, Q3 = 1,
                  include.label = T)

cg3<-compareGroups(s6_Arm ~ tb3_lus_pneumonia_final + tb3_xray_Final_read, 
                  data=dt,
                  method = 2, Q1 = 0, Q3 = 1,
                  include.label = T)

cg4<-compareGroups(s6_Arm ~ tb3_hospitalized + tb3_oxyTx + tb3_advOxyTx + tb3_DeathWithin30days, 
                  data=dt,
                  method = 2, Q1 = 0, Q3 = 1,
                  include.label = T)

cg<-rbind(`Demographic information` = cg1,
      `Clinical signs` = cg2,
      `Lung imaging` = cg3,
      `Clinical care` = cg4)

tbl<-createTable(cg, hide.no = "No", digits = 0, show.n = T, show.ratio = FALSE)
print(tbl, which.table = "both", )
export2xls(tbl, file='2022-12-15_HAPIN_Pneumonia_Table 3.xlsx', which.table = "both") 
```
